---
title: "LBB P4DS"
author: "Emannuelle Alpha Sony"
date: "7/15/2021"
output:
  html_document:
    theme: cosmo
    highlight: breezedark
    toc: true
    toc_float:
      collapsed: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# *This is my report of exploring retail data for my LBB*

## Reading Data

```{r}
retail <- read.csv("data_input/retail.csv")
```

## Data Wrangling

```{r}
library(dplyr)
retail <- retail %>% 
  mutate(Ship.Mode = as.factor(Ship.Mode), Category = as.factor(Category), Sub.Category = as.factor(Sub.Category), Segment = as.factor(Segment))
retail$Order.Date <- as.Date(retail$Order.Date,
                             "%m/%d/%y")
retail$Ship.Date <- as.Date(retail$Ship.Date,
                             "%m/%d/%y")
anyNA(retail)
head(retail)
retail_clean <- retail %>% 
  select(Order.Date, Ship.Date, Ship.Mode, Segment, Category, Sub.Category, Product.Name, Sales, Quantity, Discount, Profit)
head(retail_clean)
```

*In this section, I clean my data using DPLYR Package to make it easier and faster.*

While cleaning the data, I did some changing in data type and also selecting the needed columns and removing columns that I don't need.

## Subsetting

In this section I wanna know:
1. Products that give big profit
2. Products that give big loss

```{r}
retail_clean %>% 
  filter(Profit > 4500 | Profit < -4500)
```

## Adding New Column

From the result above, I wanna make a new column about the profit status

```{r}
retail_clean$Profit.Loss <- as.factor(ifelse(retail_clean$Profit < 0, "Loss", "Profit"))
head(retail_clean)
```
## Analyzing

From the final data. I want to analyze the data.

1. Profits that are more than 2000 and is from the "Consumer" Segment
2. Profits that are more than 2000 and is from the "Coorporate" Segment
3. Profits that are more than 500 and is from the "Furniture" Category

```{r}
retail_clean %>% 
  filter(Segment == "Consumer",
         Profit >= 2000)
```
```{r}
retail_clean %>% 
  filter(Category == "Furniture",
         Profit >= 500)
```
```{r}
retail_clean %>% 
  filter(Segment == "Consumer",
         Profit >= 500)
```
## Summary

There are a few ways to pull a summary from a data and one of them is the "summary" function

```{r}
summary(retail_clean)
```
Here you can see the min, median, max, mean, and etc.

## Data Aggregating

Here are some examples for aggregating

1. Table
```{r}
table(retail_clean$Category, retail_clean$Segment == "Consumer")
```
2. Prop.Table
```{r}
round(prop.table(table(retail_clean$Category, retail_clean$Segment))*100, digits = 2)
```
3. XTabs
```{r}
# Profits each category and segment
xtabs(formula = Profit ~ Category + Segment, data = retail_clean)
```
4. Aggregate
```{r}
#  Profit's mean each category and segment
aggregate(formula = Profit ~ Category + Segment, data = retail_clean, FUN = mean)
#  Top profit's mean each segment and category
aggregate(formula = Profit ~ Category + Segment, data = retail_clean, FUN = max)
# Top loss' mean each segment and category
aggregate(formula = Profit ~ Category + Segment, data = retail_clean, FUN = min)
```

**Maybe that is all for my little explanation of my retail data for my LBB. Thank you.**
